---
title: "Project Statical Inference"
author: "William Paredes"
date: "24/7/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sampling values in the project.


```{r include=FALSE}
library(tidyverse)
```


```{r echo=TRUE}
lambda <- 0.2 # Set lambda = 0.2 for all of the simulations.
n <- 40  # You will investigate the distribution of averages of 40 exponentials.
simulations <- 1000 # You will need to do a thousand simulations.

```

## Run Simulation 

```{r echo=TRUE}

sim_expect <- replicate(simulations, rexp(n,lambda))

```


## Find the means

```{r}

mean_expect <- apply(sim_expect, 2, mean)

```

## Histogram


```{r echo=TRUE}
hist(mean_expect, breaks = n, main = "Project expotential distribution")
```


# 1.Show the sample mean and compare it to the theoretical mean of the distribution.

```{r echo=TRUE}

mean(mean_expect)
hist(mean_expect, breaks = n, main = "Sample mean - Theoretical mean")
abline(v = mean(mean_expect), col = "green", lwd = 2)


```


# 2.Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.

### The variances is very close.

```{r}
#Sample Variance

sd(mean_expect)^2

#Theoretical Variance

(1/lambda / sqrt(n))^2
tv <- (1/lambda / sqrt(n))^2


```


# 3.Show that the distribution is approximately normal.

### The plot shows a normal distribution to the Central Limit Theorem.

```{r echo=TRUE}

hist(mean_expect, prob=TRUE,main="Distribution", breaks=n, xlim=c(2,9))
lines(density(mean_expect), col="red",lwd=2)
x <- seq(min(mean_expect), max(mean_expect), length.out = 2*n)
y <- dnorm(x, mean = 1/lambda, sd = sqrt(tv))
lines(x,y,lwd = 2, col = "black", lty = 2)

```





